**The Place of Interoception and Theory of Mind in Deception**

### 2021-11-24 4_Intero.Rmd
fix images

  p_rt_maia_notworrying + 
  p_rt_maia_emotionalawareness / 
  p_rt_maia_attentionregulation / 
  p_rt_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))

@@

p_hr_maia_notworrying + 
  p_hr_maia_emotionalawareness / 
  p_hr_maia_attentionregulation / 
  p_hr_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))
```

>>>>

  p_rt_maia_notworrying / 
  p_rt_maia_emotionalawareness / 
  p_rt_maia_attentionregulation / 
  p_rt_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))

@@

p_hr_maia_notworrying / 
  p_hr_maia_emotionalawareness / 
  p_hr_maia_attentionregulation / 
  p_hr_maia_selfregulation +
  patchwork::plot_annotation(title = "Interoception (MAIA) 2/2", theme = theme(plot.title = element_text(hjust = 0.5)))
```
